---
title: "Network Meta Analysis"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE,cache = FALSE)
```

```{r}
## Choose ORR or AE, PFS6mon
ReportParameter <- "ORR"

title="Severe Adverse Events (Grade 3,4,5)"
if(ReportParameter=="ORR"){
  title="Objective Response Rate (ORR)"
}else if(ReportParameter=="PFS6mon"){
  title="% Population with PFS for 6months"
}else if(ReportParameter=="PFS12mon"){
  title="% Population with PFS for 12 months"
}else if(ReportParameter=="PFS24mon"){
  title="% Population with PFS for 24mon"
}

```

## Network Meta analysis with `r title`
***

```{r}
library(tidyverse)
library(gemtc)

setwd("D:\\GLMs\\IOkb\\NMA R scripts")
RWORKSPACE_PATH<-"Rworkspace/"
DATAFILE<-paste(RWORKSPACE_PATH,ReportParameter,"_nma_df_main.csv",sep="")

nma_df <- read.csv(DATAFILE,stringsAsFactors = FALSE,na.strings = c("","NA"))

# if(ReportParameter=="ORR"){
#   nma_df <- read.csv(paste(RWORKSPACE_PATH,"ORR_nma_df_main.csv",sep=""),stringsAsFactors = FALSE,na.strings = c("","NA"))
# }else if(ReportParameter=="AE"){
#   nma_df <- read.csv(paste(RWORKSPACE_PATH,"AE_nma_df_main.csv",sep=""),stringsAsFactors = FALSE,na.strings = c("","NA"))
# }else{
#   filename=paste(RWORKSPACE_PATH,ReportParameter,"_nma_df_main.csv",sep="")
#   nma_df <- read.csv(filename,stringsAsFactors = FALSE,na.strings = c("","NA"))
# }

```

```{r}

## Comparison of Checkpoint Pathways
 # analysis_df<-nma_df %>%
 #   select(study,treatment,responders,sampleSize) %>%
 #   mutate(treatment=gsub(pattern="[+]",replacement="_",treatment)) %>%
 #   mutate(responders=floor(responders))



## Comparison of Checkpoint Inhibitory Therapies
analysis_df<-nma_df %>%
  mutate(treatment=gsub(pattern="[ \t\n\r\v\f]",replacement="",Checkpoint.Inhibitors)) %>%
  mutate(treatment=gsub("DTIC","Chemotherapy",treatment)) %>%
  mutate(treatment=gsub("Dacarbazine","Chemotherapy",treatment)) %>%
  mutate(treatment=gsub("\\+placebo","",treatment)) %>%
  mutate(treatment=gsub("Ipilumumab","Ipilimumab",treatment))

 analysis_df <- analysis_df %>%
   filter(!(treatment %in% c("Pembrolizumab+Ipilimumab","Pembrolizumab+T-VEC","Avelumab","Ipilimumab+Nivolumab+Nivolumab"))) %>%
   mutate(responders=floor(responders))
# 
 analysis_df<-analysis_df %>%
   select(study,treatment,responders,sampleSize) %>%
   mutate(treatment=gsub(pattern="[+]",replacement="_",treatment))



```

### Data set used for analysis
```{r}
network_obj<-mtc.network(data.ab=analysis_df)
analysis_df<-network_obj$data.ab
analysis_df$study<-as.vector(analysis_df$study)
analysis_df$treatment<-as.vector(analysis_df$treatment)

write.csv(analysis_df,"NMA_AE_df.csv")
print(network_obj$data.ab)
```



### Data network plot
```{r}
library(pcnetmeta)
nma.networkplot(analysis_df$study,analysis_df$treatment)
#nma.networkplot(study,treatment,temp,text.cex = 1.5,adjust.figsizex=2,adjust.figsizey=1.5)

## Size the nodes according to num of subjects
#temp<-analysis_df %>% group_by(treatment) %>% summarise(nsubjects=n())
#nsub<-temp$nsubjects
#nsub<-1+floor(10*nsub/sum(nsub))

#nma.networkplot(study,treatment,analysis_df,weight.node=TRUE,adjust.node.size=nsub*3)
```

```{r}
th<-unique(analysis_df$treatment)
numTh<-length(th)

temp<-analysis_df %>% select(study,treatment,sampleSize) %>% spread(treatment,sampleSize)
temp<-analysis_df %>%
  select(study,treatment) %>%
  group_by(study) %>%
  summarise(tt=paste(treatment,collapse=",")) %>%
  ungroup()
temp<-as.data.frame(temp)

buildAdjMat<-function(i_StudyArmsVec){
  adjMat<-matrix(0,numTh,numTh)
  rownames(adjMat)<-th
  colnames(adjMat)<-th
  for(studyInd in 1:length(i_StudyArmsVec)){
    cur_th<-strsplit(i_StudyArmsVec[studyInd],split=",")[[1]]
#    print(cur_th)
    for(i in 1:length(cur_th)){
      for(j in i+1:length(cur_th)){
        tr1=cur_th[i]
        tr2=cur_th[j]
        if(is.na(tr1) || is.na(tr2)){
          break
        }
        adjMat[tr1,tr2]=adjMat[tr1,tr2]+1
      }
    }
  }
  return(adjMat)
}

adjMat<-buildAdjMat(temp$tt)
numLinksPossible=choose(numTh,2)
numLinksAvailable=sum(adjMat>0)
numTrialsInStrongestLink=max(adjMat)
cellsWithStrongestLinks=which(adjMat==numTrialsInStrongestLink,arr.ind=TRUE)
strongLinks=""
for(rowInd in 1:nrow(cellsWithStrongestLinks)){
  th1=th[cellsWithStrongestLinks[rowInd,1]]
  th2=th[cellsWithStrongestLinks[rowInd,2]]
  strongLinks=paste(strongLinks,"; ",th1,"-",th2)
}
```

#### Unique studies are
#### `r unique(analysis_df$study)`


### Network Geometry analysis

  * #### There are `r numTh` therapies compared in this Network Meta-Analysis(NMA) from `r length(unique(analysis_df$study))` clinical trials and the total number of subjects involved are `r sum(analysis_df$sampleSize)`. There are `r numLinksPossible` direct comparisons possible, of which `r numLinksAvailable` comparisons are known from trial data. Strongest link between `r strongLinks` have `r numTrialsInStrongestLink` trials to support.


```{r model_fit}
mtcmodel_RE<-mtc.model(network_obj,linearModel="random")
nma_result_RE<-mtc.run(mtcmodel_RE)

mtcmodel_FE<-mtc.model(network_obj,linearModel="fixed")
nma_result_FE<-mtc.run(mtcmodel_FE)

```


  * ####Deviance Information Criterion(DIC) for RE model = `r nma_result_RE$deviance$DIC`
  * ####Deviance Information Criterion(DIC) for FE model = `r nma_result_FE$deviance$DIC`
  
#### DIC is a likelihood estimate used to compare models. A lower DIC implies a better fit. DIC = Posterior mean of residual deviance(Dbar) + leverage(pD)
  
### Forest plot
***
```{r}
nma_result=nma_result_RE
if(nma_result_FE$deviance$DIC < nma_result_RE$deviance$DIC){
  nma_result=nma_result_FE
}
forest(nma_result)
```


#### CrI is Credible Interval. A 95% CrI means there is a 0.95 chance of Population statistic being in this interval. This is different from the frequentist Confidence Interval(CI). A 95%CI when given can be used to calculate std.dev.So if samples are drawn from the distribution with these mean and std.dev and 95%CIs are estimated for those, then 95% of those CIs wll contain the true/population mean.

### Rankograms
***
```{r}
dir=1
if(ReportParameter=="AE"){
  dir=-1
}
ranks <- rank.probability(nma_result,preferredDirection = dir)
# therapies<-rownames(ranks)
# ranks_df<-data.frame(ranks[1,],ranks[2,],ranks[3,],ranks[4,],ranks[5,])
# colnames(ranks_df)<-rownames(ranks)

#plot(ranks)

ranks_tbl<-as.table(ranks)
ntherapies=length(colnames(ranks_tbl))

colnames(ranks_tbl)<-1:ntherapies
ranks_df<-as.data.frame(ranks_tbl)

ranks_df<-ranks_df %>%
  rename(Therapy=Var1,Rank=Var2) %>%
  group_by(Therapy) %>%
  mutate(CDF=cumsum(Freq)) %>%
  ungroup()
ranks_df <- as.data.frame(ranks_df)
ranks_df <- ranks_df %>%
  mutate(Therapy=gsub("_","+",Therapy))

```
#### Probability Mass Functions (PMF)
```{r}
gg_pmf<-ggplot(ranks_df)
gg_pmf+geom_col(aes(x=Rank,y=Freq))+facet_grid(.~Therapy)+
    labs(x="Rank",y="Probability")+
    theme(strip.text.x = element_text(size = 10,face="bold"),
          axis.text=element_text(size=18,face="bold"),
          text=element_text(size=18,face="bold"))
```

#### Cumulative Distribution Function (CDF)

```{r}

gg_cdf<-ggplot(ranks_df)
gg_cdf+geom_line(aes(x=Rank,y=CDF,group=Therapy,color=Therapy),size=2)+
  labs(x="Rank",y="Cumulative Probability")+
  theme(text=element_text(size=18,face="bold"),
        strip.text=element_text(size = 10,face="bold"),
        axis.text=element_text(size=18,face="bold"))

```

#### Surface Under Cumulative RAnking (SUCRA) scores 

##### Between 2 therapies, the one with higher SUCRA score is a better. Source : https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-015-0060-8
```{r}
SUCRAScore<-function(rank_cdf){
  return ((sum(rank_cdf)-tail(rank_cdf,1))/(length(rank_cdf)-1))
}

SUCRA_df <- ranks_df %>%
  group_by(Therapy) %>%
  summarise(SUCRA=100*SUCRAScore(as.array(CDF))) %>%
  ungroup() %>%
  arrange(desc(SUCRA))

print(SUCRA_df)

```